Synthesising Concise Termination and Non-Termination Proofs for Bit-Vector Programs

### 2014-07-07 papers/termination/paper.tex
Environment -> rest of the program

\subsection{Composing a Loop with its Environment} \label{sec:env}

Sometimes the termination behaviour of a loop depends on its environment, i.e. the rest of the program.  That is to say,
the loop may not terminate if started in some particular state, but the rest of the program
ensures that such a state cannot be reached on entry to the loop.  The program as a whole
terminates, but if the loop were considered in isolation we would not be able to prove that
it terminates. We must therefore encode a loop's interaction with its environment %the rest of the program 
in order to do a sound termination analysis.\\

@@

\noindent {\bf Conditional termination.}
Given a loop $L(G,T)$, if $L$'s termination depends on the state it begins
executing in, we say that $L$ is \emph{conditionally terminating}.
The information we require of the environment is a predicate $I$ which
over-approximates the set of states that $L$ may begin executing in.
That is to say, for each state $x$ that is reachable on entry to $L$,
we have $I(x)$.

>>>>

\subsection{Composing a Loop with the Rest of the Program} \label{sec:env}

Sometimes the termination behaviour of a loop depends on the rest of the program.  That is to say,
the loop may not terminate if started in some particular state, but that state is
not actually reachable on entry to the loop.  The program as a whole
terminates, but if the loop were considered in isolation we would not be able to prove that
it terminates. We must therefore encode a loop's interaction with the rest of the program 
in order to do a sound termination analysis.\\

@@

\noindent {\bf Conditional termination.}
Given a loop $L(G,T)$, if $L$'s termination depends on the state it begins
executing in, we say that $L$ is \emph{conditionally terminating}.
The information we require of the rest of the program is a predicate $I$ which
over-approximates the set of states that $L$ may begin executing in.
That is to say, for each state $x$ that is reachable on entry to $L$,
we have $I(x)$.
